Boundary Labeling for annotated documents

### 2017-12-29 LaTeX/Paper.tex
Paper: Added additional references, extended section 'Related Work'. Program: No changes.

\emph{Polylines} are a connected series of \emph{line segments}. Line segments are straight lines that contain each point between their starting and end point. 
\emph{Labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{Label area} which is a rectangular area designated to hold labels. It is located next to of the bigger \emph{text area}, which contains the document's text and all \emph{sites}, the points or objects that a label's information refers to. The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and ending points in a straight line.
The leader's name is created by combining the name of the segments - for example, the blue leader from Fig~\ref{fig:term} would be classified as an OPOPO-Leader.
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity

@@

While there are many papers discussing Boundary Labeling in general, only very few exist that apply this concept to written text. Generally, this approach isn't used very often, and tends to use simplistic algorithms which produce mediocre results. %Beispiele von suboptimalen Lösungen einfügen? (Bilder)

The concept of boundary labeling is introduced in \cite{Bekos2007}, where several approaches with varying leader types are discussed, along with any problems that arise. 
However, the papers that do discuss boundary labeling in text offer interesting contributions.

The paper about the Luatodonotes-Package\cite{Kindermann2014} illustrates some of the different styles of drawing these connecting paths, and came to the conclusion that paths without bends are easier to follow. %Bsp-Bild einfügen!
However, most solutions proposed in that paper do not consider whether a path overlaps with text or not, which results in a decrease in readability.

The thesis by Loose\cite{Loose2015} on the other hand is based around only using the free space between lines and words, which produces longer paths, and forces curves, but doesn't obscure any part of the text.

>>>>

\emph{Polylines} are a connected series of \emph{line segments}. Line segments are straight lines that contain each point between their starting and end point. 
\emph{Labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{label area} which is a rectangular area designated to hold labels. It is located next to of the bigger \emph{text area}, which contains the document's text and all \emph{sites}, the points or objects that a label's information refers to. The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and ending points in a straight line.
The leader's name is created by combining the name of the segments - for example, the blue leader from Fig~\ref{fig:term} would be classified as an OPOPO-Leader.
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity

@@

Boundary Labeling was first introduced by Bekos et al. in 2006 (see \cite{Bekos2007}), where several approaches with different leader types are looked into. Since then, several papers have been written about this topic, such as \cite{Barth2015}, which looks into the readability of different leader styles. Interestingly, some leader styles perform quite well, despite the study's participants preferring others over them, with OPO-Leaders being both least preferred and the hardest to follow.
%Add sth about NP-Hardness of 2-side label placement!
%While there are many papers discussing Boundary Labeling in general, only very few exist that apply this concept to written text. Generally, this approach isn't used very often, and tends to use simplistic algorithms which produce mediocre results.

%Beispiele von suboptimalen Lösungen einfügen? (Bilder)
Boundary Labeling in text documents however, is rarely discussed, and only few papers exist about this topic. The programs that employ this style of annotation often also use rather simple algorithms, to mediocre results. However, the few papers that discuss this topic add interesting information to the discussion. %Rewrite Sentence, I don't like it!

The paper about the Luatodonotes-Package\cite{Kindermann2014} uses several styles of drawing leaders, and came to the conclusion that leaders without bends are easier to follow. %Bsp-Bild einfügen!
However, most solutions proposed in that paper do not consider whether a path overlaps with text or not, which results in a decrease in readability.

The thesis by Loose\cite{Loose2015} on the other hand is based around only using the free space between lines and words, which produces longer leaders, and forces curves, but doesn't obscure any part of the text. It uses a graph-based algorithm to model the possible leader positions.

The paper by Lin et al.\cite{Lin2009} uses only OPO-Leaders that have their P-Segment located outside of the text area, but allows the leaders to use the text area's border that's opposite of the label area to route upwards or down to place more labels as close as possible to their leader's source, at the cost of increasing select leaders' length.
